Abstract Data Type Inference

### 2015-03-12 algorithm.tex
Added Theorem 1.
Better definition of weight, includes duplicates.

In addition to the relations $\to_\mathrm{o}$, $\to_\mathrm{p}$, and
$\to_\mathrm{c}$ of Section~\ref{sec:histories} under which all ADTs are
closed, the ADTs we consider in this work are also closed under additional
relations which remove matches, and duplicate operations. Given a history
$\tup{O,<,c,f,m}$, we say an operation $o \in O$ is a \emph{duplicate} if there
exists another operation $o' \in O$ with the same labels and matching: $c(o) =
c(o')$, $f(o) = f(o')$, and $m(o) = m(o')$. The relations $\to_\mathrm{m}$ and
$\to_\mathrm{d}$ relate two histories $h_1$ and $h_2$ when $h_2$ is obtained
from $h_1$ by
\begin{itemize}

@@

Computing $B$ thus amounts to computing its finite representation. In general,
this is achieved by enumerating the elements of $B$ while maintaining the
$\preceq$-minimal elements, and recognizing a condition under which all
elements of $B$ are related to the current set of
minimals~\cite{conf/lics/AbdullaCJT96, journals/tcs/FinkelS01}. In our case, we
recognize a condition on the weight-increasing enumeration of $B$ which
guarantees coverage by the current set of minimals. Formally, for all $i \in
\mathbb{N}$, we define
\begin{align*}
  B_i &= \set{ h \in B : \weight h \le i } \\
  B_i' &= \set{ h' \in B :
    \exists h \in B_i.\ h \preceq h' \text{ and } \weight h \le i+1
  }
\end{align*}
as, respectively, the histories of $B$ with at most $i$ matches, and those
derived from $B_i$ with at most $i\!+\!1$ matches. We say that $A$ is
\emph{predictable} if $B_i = B$ whenever $B_i' = B_{i+1}$. In 
Section~\ref{sec:nature} we demonstrate that naturally-occurring ADTs are
predictable. Since the number of weight-$i$ histories is finite\footnote{As
noted in Section~\ref{sec:histories}, we consider equality between histories up
to renaming of operation identifiers.} for each $i \in \mathbb{N}$, each $B_i$
is computable.

@@

>>>>

In addition to the relations $\to_\mathrm{o}$, $\to_\mathrm{p}$, and
$\to_\mathrm{c}$ of Section~\ref{sec:histories} under which all ADTs are
closed, the ADTs we consider in this work are also closed under additional
relations which remove matches, and duplicate operations. The relations
$\to_\mathrm{m}$ and $\to_\mathrm{d}$ relate two histories $h_1$ and $h_2$ when
$h_2$ is obtained from $h_1$ by
\begin{itemize}

@@

Computing $B$ thus amounts to computing its finite representation. In general,
this is achieved by enumerating the elements of $B$ while maintaining the
$\preceq$-minimal elements, and recognizing a condition under which all
elements of $B$ are related to the current set of
minimals~\cite{conf/lics/AbdullaCJT96, journals/tcs/FinkelS01}. In our case, we
recognize a condition on the weight-increasing enumeration of $B$ which
guarantees coverage by the current set of minimals. Formally, for all $i \in
\mathbb{N}$, we define
\begin{align*}
  B_i &= \set{ h \in B : \weight(h) \le i } \\
  B_i' &= \set{ h' \in B :
    \exists h \in B_i.\ h \preceq h' \text{ and } \weight(h) \le i+1
  }
\end{align*}
as, respectively, the histories of $B$ with at most $i$ matches and duplicates,
and those derived from $B_i$ with at most $i\!+\!1$ matches and duplicates. We
say that $A$ is \emph{predictable} if $B_i = B$ whenever $B_i' = B_{i+1}$. In
Section~\ref{sec:nature} we demonstrate that naturally-occurring ADTs are
predictable. Since the number of weight-$i$ histories is finite\footnote{As
noted in Section~\ref{sec:histories}, we consider equality between histories up
to renaming of operation identifiers.} for each $i \in \mathbb{N}$, each $B_i$
is computable.

@@

TODO DESCRIBE HOW TO GET THE FORMULA $F$ FROM $B$, AND ARGUE THAT WE HAVE
SOLVED THE PROBLEM.

\begin{theorem}

  “The symbolic ADT inference problem is computable for normal ADTs.”

\end{theorem}

### 2015-03-12 histories.tex
Better definition of weight, includes duplicates.

\end{itemize}
Non-completed operations are \emph{pending}, and are maximal in the
happens-before order. The \emph{width} of a history is the maximum number of
its operations which are mutually unordered, and the \emph{width} of a history
set is the maximum width of its elements. Width-$1$ histories are
\emph{sequential}. An operation $o \in \rng(m)$ is a \emph{match target}, and
the set $\set{ o' \in O : m(o') = o}$ of operations targeting $o$ is a
\emph{match}. We assume targets target themselves: $m(o) = o$ for $o \in
\rng(m)$. The \emph{weight} of $h$ is the number $|\rng(m)|$ of matches.
Since the operation identifiers of a history have no intrinsic meaning, we
consider equality between histories up to renaming of operation identifiers.

>>>>

\end{itemize}
Non-completed operations are \emph{pending}, and are maximal in the
happens-before order. The \emph{width} of a history is the maximum number of
its operations which are mutually unordered, and the \emph{width} of a history
set is the maximum width of its elements. Width-$1$ histories are
\emph{sequential}. Two operations with the same labels and matching are
\emph{identical}, and the \emph{frequency} of an operation $o$, denoted
$\freq(o)$, is the number of operations identical to $o$, including $o$ itself.
An operation is a \emph{duplicate} when $\freq(o) > 1$. An operation $o \in
\rng(m)$ is a \emph{match target}, and the set $\set{ o' \in O : m(o') = o}$ of
operations targeting $o$ is a \emph{match}. We assume targets target
themselves: $m(o) = o$ for $o \in \rng(m)$. The \emph{weight} of $h$ is the
maximum $\max(\set{ \freq(o) : o \in O } \cup \set{|\rng(m)|})$ between
operation frequencies and the number of matches. Since the operation
identifiers of a history have no intrinsic meaning, we consider equality
between histories up to renaming of operation identifiers.
